\jaxcosmo: An End-to-End Differentiable and GPU Accelerated Cosmology Library

### 2022-11-13 paper_OJA.tex
table caption left aligned

@@

The first approach is to derive analytically the formula for the derivatives of interest \citep{BORG}, with or without the help of tools such as \texttt{Mathematica}. This is however only practical typically for simple analytical models.

>>>>

\usepackage[
singlelinecheck=false % <-- important
]{caption}

@@

The first approach is to derive analytically the formula for the derivatives of interest \citep{2019A&A...625A..64J} \JEC{This reference should be validated by F.L}, with or without the help of tools such as \texttt{Mathematica}\footnote{\url{https://www.wolfram.com/mathematica}.}. This is however only practical typically for simple analytical models.
